Redshift evolution of the SN stretch distribution

### 2019-10-14 Nicolas.tex
Petites modif, gitignore

\section{Sample}
We use data from 5 different surveys, 3 of which had selection effects that we
tried to remove with a statistical approach in lack of precise data concerning
the instruments' capacity to acquire fluxes. Here it is:

>>>>

\section{Sample}
We use data from 5 different surveys: Hubble Space Telescope (HST, REF),
Supernova Nearby Factory (SNf, REF), Supernova Legacy Survey (SNLS, REF), Sloan
DSS (SDSS, REF) and Panstarr-1 (PS1, REF). 3 of which had selection effects that
we tried to remove with a statistical approach in lack of precise data
concerning the instruments' capacity to acquire fluxes. Here it is:
